### 2014-07-08 trunk/documents/thesis/Capitulo_5.tex

%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,letterpaper,english,12pt,english,openany,letterpaper,pagesize]{scrbook}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}
\usepackage{float}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{esint}
\onehalfspacing

@@

@@

\usepackage{babel}
\begin{document}
\pagenumbering{roman}
\begin{center}
\begin{figure}
\centering%
%\includegraphics[width=0.4\columnwidth]{resources/logo_un.png}
%\includegraphics[width=0.4]{logo_un.png}
\end{figure}
\thispagestyle{empty}

\vspace{2cm}

\textbf{\huge Adapted Laplacian Operator For Hybrid Quad/Triangle
Meshes}{\huge \par}

\vspace{6cm}

\textbf{\large Alexander Pinzón Fernández}{\large \par}

\vspace{6cm}

Universidad Nacional de Colombia

Facultad de Ingenieria, Departamento de Sistemas e Industrial

{\small Grupo de Investigación CIM@LAB}{\small \par}

Bogotá, Colombia

2014

\end{center}

\newpage{}

\begin{center}
\thispagestyle{empty} 
\vspace*{0cm}

\textbf{\huge Adapted Laplacian Operator For Hybrid Quad/Triangle
Meshes}{\huge \par}

\vspace{2.5cm}

\textbf{\large Alexander Pinzón Fernández}{\large \par}

\vspace{2.5cm}

{\small A thesis submitted in partial fulfillment of the requirements
for the degree of:}{\small \par}

\textbf{Master in Systems Engineering and Computer Science}

\vspace{2cm}

{\small Advisor:}\\
{\small Eduardo Romero Castro , Ph.D.}{\small \par}

{\small \vspace{1.5cm}
}{\small \par}

{\small Research Area:}\\
{\small Computer Graphics}{\small \par}

{\small \vspace{2cm}
}{\small \par}

{\small Universidad Nacional de Colombia}\\
{\small Facultad de Ingenieria, Departamento de Sistemas e Industrial}\\
{\small Grupo de Investigación CIM@LAB}\\
{\small Bogotá, Colombia}\\
{\small 2014}{\small \par}

\end{center}
\newpage 
\thispagestyle{empty}

\textbf{Dedicación}

{\small \vspace{4cm}
}{\small \par}

\noindent \begin{flushright}
\begin{minipage}[t]{8cm}%
{\small A Beatriz y Campo Elias mis padres que siempre me dieron la
libertad de escoger, con su comprensión y apoyo me permitieron dedicar
mi tiempo a la ciencia.}{\small \par}

{\small \vspace{1cm}
}{\small \par}

{\small A mis padres}{\small \par}

{\small \vspace{1cm}
}{\small \par}

Beatriz Fernandez Vargas

Campo Elias Pinzon Rojas%
\end{minipage}
\par\end{flushright}

\newpage
\thispagestyle{empty}

\textbf{\LARGE Acknowledgement}{\LARGE \par}

\addcontentsline{toc}{chapter}{\numberline{}Acknowledgement}

\vspace{2cm}

I wold like to thank my advisor professor Eduardo Romero and CIM\&LAB
research group for his support in this thesis.

{\small \vspace{1cm}
}{\small \par}

I would like to thank all the workers in Colombia who fund the public
education with their work.

{\small \vspace{1cm}
}{\small \par}

This work was supported in part by the Blender Foundation, Google
Summer of code program at 2012 - 2013.

\newpage{}

\textbf{\LARGE Abstract}{\LARGE \par}

\addcontentsline{toc}{chapter}{\numberline{}Abstract}

In the last two decades three-dimensional modeling methods have been
evolving and developing rapidly, thanks in part to the use of vector
operators of differential geometry. The Laplacian operator has been
one of the most widely studied and used thanks to the properties exhibited
by their eigenvectors in novel applications such as noise reduction,
enhancement, remeshing, UV mapping, posed, skeletonization, among
other. The differential operator is defined in a continuous and smooth
domain named manifold, manifolds are often approximated by discrete
polygon meshes composed by triangles and quadrangles which represent
the real world three-dimensional objects. In these meshes spectral
structure is calculated using a discrete Laplacian operator, the discrete
version of the Laplacian operator given by Pinkall in 1993 works only
with meshes of triangles, and Xiong in 2011 working exclusively with
quads. This thesis proposes an original extension of the Laplacian
operator that allows to work with hybrid meshes composed by triangles
and quadrangles.

Along with the operator, this work presents new sculpting and modeling
applications with base on the enhancement, applications on subdivision
surfaces using smoothing, mesh posing using differential coordinates
and skeletonization using iterative contraction. This series of applications
demonstrates the quality, predictability and flexibility of the proposed
operator.

The proposed operator was successfully used in real production environments
within software Blender how new tools. Currently these tools are available
as open source software.

\textbf{\LARGE Resumen}{\LARGE \par}

En las dos últimas décadas los métodos de modelado tridimensional
han ido evolucionando y desarrollándose rápidamente, en parte gracias
al uso de operadores vectoriales de geometría diferencial. El operador
Laplaciano ha sido uno de los más ampliamente estudiado y usado gracias
a las propiedades exhibidas por sus vectores propios en novedosas
aplicaciones como: reducción de ruido, realce, remallado, mapeo UV,
posado, esqueletonización, entre otras. Este operador diferencial
es definido en un dominio continuo y suave llamado variedad, las variedades
son a menudo aproximadas por mallas discretas de polígonos compuestas
por triángulos y cuadrángulos que a su vez representan objetos tridimensionales
del mundo real. En estas mallas se calcula la estructura espectral
con el uso de algún operador Laplaciano discreto, la versión discreta
del operador Laplaciano propuesta por Pinkall en el 1993 trabaja únicamente
con mallas compuestas por triángulos, y la de Xiong en el 2011 trabaja
exclusivamente con cuadrángulos. Esta tesis propone una extensión
original del Operador Laplaciano que permite trabajar con mallas híbridas
compuestas por triángulos y cuadrángulos.

Junto con el operador, este trabajo presenta nuevas aplicaciones en
esculpido y modelamiento con base en el realce, aplicaciones en subdivisión
de superficies con el uso de suavizado, posado de mallas con el uso
de coordenadas diferenciales y esqueletonización usando contracción
iterativa. Esta serie de aplicaciones demuestra la calidad, predictibilidad
y flexibilidad del operador propuesto.

El operador propuesto fue usado de forma exitosa en ambientes reales
de producción dentro del software Blender como nuevas herramientas.
Actualmente estas herramientas están disponibles como programas de
código abierto.

{\small \vspace{1cm}
}{\small \par}

\textbf{\small Keywords: laplacian operator; smooth; enhance; sculpting;
subdivision surface}{\small \par}

\tableofcontents{}

\listoffigures

\listoftables

\pagenumbering{arabic}

\chapter{Introduction}

The discrete versions of Laplace Beltrami Operator have been used
in the last years for the develop of new geometric modeling tools.
In the work of Pinkall \cite{Pinkall1993} was introduced the cotangent
version of Laplace operator, that allow to find the minimal surface
when compute a discete harmonic map with the Laplacian operator, this
version has been widely studied and applied in various problems of
computer geometric modeling. The manifolds that are continuous domains
homeomorphic to $\mathbb{R}^{n}$ are represented in computers by
polygon meshes. These polygons are generally composed of triangles
and quadrangles, while work with laplacian operator in this hybrid
composition are not a mathematical challenge, most research uses only
meshes composed by triangles \cite{Pinkall1993,Desbrun1999,Meyer2003,Sorkine2004,Au2008,Belkin2008,Hahne2006},
in other recent studies \cite{Liu2008,Xiong2011} the Laplacian operator
is working exclusively with quadrangles. But in the artistic scope
topology and the way the edges are distributed, the triangle and quadrangles,
directly affects the processes of animation, interpolation, textured,
etc. As discussed by \cite{Mullen2007} who use a manual connection
of a couple of vertices to perform animation processes and interpolation.
It is then of paramount importance to develop operators that easily
interact with such meshes, eliminating the need of preprocessing the
mesh to convert it to triangles and change the original topology.

Modeling techniques able to generate a variety of realistic shapes,
have been developed \cite{Botsch2006}. Editing techniques have evolved
from affine transformations to advanced tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
based methods however require to interact with a minimun number of
control points for any operation to be efficient, or in other words,
a unicity condition is introduced by demanding a smooth surface after
any of these shape operations. Hence, traditional modeling methods
for subdividing surfaces from coarse geometry have become widely popular
\cite{Catmull1978,Stam1998}. These works have generalized a uniform
B-cubic spline knot insertion to meshes, some of them adding some
type of control, for instance with the use of creases to produce sharp
edges \cite{DeRose1998}, or the modification of some vertex weights
to locally control the zone of influence \cite{Biermann2000}. Neverteless
these methods are difficult to deal with since they require a large
number of parameters and a very tedious customization. Instead, the
presented applications requires a single parameter that controls the
global curvature, which is used to maintain realistic shapes, creating
a family of different versions of the same object and therefore preserving
the detail of the original model and a realistic appearance.

The shape inflation and shape exaggeration can thus be used as such
brush in the sculpting process, when inflating a shape since current
brushes end up by losing detail when moving vertices \cite{Stanculescu2011}.
In contrast, the presented enhance method inflates a mesh by moving
the vertices towards the reverse curvature direction, conserving the
shape and sharp features of the model.

\paragraph{Contributions}

This work presents an extension of the Laplace Beltrami Operator for
hybrid quad/triangle meshes, representing a larger mesh spectrum from
what has been presented so far. The method eliminates the need of
preprocessing and allows preservation of the original topology. Likewise,
along with this operator, it is proposed a method to generate a family
of parameterized shapes, in a robust and predictable way. This method
enables customization of the smoothness and curvature, obtained during
the subdivision surfaces process. Finally, it is proposed a new brush
for inflating the silhouette mesh features in modeling and sculpting.

This work is organized as follows: Chapter \ref{sub:1.1-Related-work}
presents works related to the Laplacian operator, applications in
digital sculpting, deformation, and offsetting methods for polygonal
meshes; In chapter \ref{chap:Mathematical-foundation}, it is described
the theoretical framework of the Laplacian operator for polygon meshes;
In chapter \ref{sec:Proposed-Method}, it is presented the extension
of the Laplacian Operator for hybrid meshes and applications of shape
inflation ,subdivision of surfaces , deformation, skelenotization
and sculpting; finally some Laplacian Operator results, to hybrid
quad/triangle meshes are graphically shown as well as results of the
shape inflation applications in sculpting, subdivision, deformation,
skelenotization and modeling.

\chapter{Related work\label{sub:1.1-Related-work}}

Many tools have been developed for modeling, based on the Laplacian
mesh processing. These different tools preserve the surface geometric
details when using laplacian operators for different processes such
as smoothing, enhancing, free-form deformation, fusion, morphing and
other applications \cite{Ranjan2012}.

The most used discretization of Laplace Beltrami operator $\Delta_{\mbox{\ensuremath{\Omega}}}$
over a triangulated mesh $\Omega$ was proposed by Pinkall \cite{Pinkall1993}.

\noindent \begin{center}
$\Delta_{\mbox{\ensuremath{\Omega}}}\left(u\right)=\frac{1}{2}\sum_{j\in N_{1}\left(i\right)}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\left(x_{i}-x_{j}\right)$
\par\end{center}

Where $N_{1}$is the 1-ring neighboorhood, $\alpha$ and $\beta$
are the opposite angles to edge between vertex $i$ and vertex $j$.
In this work the discretize laplacian operator was used to find the
minimal surface based on minimization energy strategy using the Dirichlet's
energy of the function $u$ over a manifold represented by triangulated
mesh $\Omega$.

\noindent \begin{center}
$E_{D}\left(u\right)=\frac{1}{2}\int_{\Omega}\bigl|\nabla u\bigr|^{2}$
\par\end{center}

Then Taubin works \cite{Taubin1995} for first time treat the problem
of noise reduction in digital poligonal meshes from signal proccessing
point of view. Taubin extends Fourier analysis to signals defined
on polygonal meshes, Taubin observe that Fourier transform is a decomposition
of the signal into an eigenvectors of the Laplacian operator, and
reconstruct the signal with a linear combination of these eigenvectors.
Desbrun works \cite{Desbrun1999} consider the same approach of Taubin,
but Desbrun use a curvature normal ($\bar{\kappa}\mathbf{n}$) based
on cotangen Laplace operator version for noise reduction over a difussion
process. This it's the most important and popular Laplace Beltrami
opertator discretization \cite{Liu2008}, many works for mesh smoothing
and fairing have been developed based on this LBO discretization \cite{Desbrun2000,Meyer2003,Schneider2001,Nealen2006}.

\noindent \begin{center}
$\frac{\partial x_{i}}{\partial t}=-\bar{\kappa_{i}}\mathbf{n_{i}}$
\par\end{center}

\noindent \begin{center}
$-\bar{\kappa_{i}}\mathbf{n_{i}}=\frac{1}{A}\sum_{j\in N_{1}\left(i\right)}\left(\cot\alpha_{j}+\cot\beta_{j}\right)$
\par\end{center}

Where $A$ is the area surrounding vertex $i$. This laplacian operator
$L$ was used for reduce the noise in a mesh $X$ over a difussion
process.

The convergence of the Laplace Beltrami operator has been very important
in fields how numerical analysis, given that implications in the simulation
process and geometric partial differentials equations. In the works
of \cite{Xu2004} is established the convergence of several discrete
Laplace Beltrami operators over triangulated meshes with numerical
results that support the theoretical analysis. Over quadrilateral
meshes Liu \cite{Liu2008} presents a discrete Laplace Beltrami Operator
based on a bilinear interpolation and its convergence over this type
of meshes composed only by quads.

In the work of Sorkine \cite{Sorkine2006} the laplacian operator
was used to repose a meshes while preserving geometry details of the
surface. The details was stored in differential coordinates $\delta_{i}$
for every vertex $v_{i}$.

\noindent \begin{center}
$\delta_{i}=\sum_{j\in N_{1}\left(i\right)}\frac{1}{2}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\left(v_{i}-v_{j}\right)$
\par\end{center}

The differential coordinates represents the difference between the
absolut coordinate of $v_{i}$and the center of mass of its immediate
neighboors.

Offset methods for polygon meshing, based on the curvature defined
by the Laplace Beltrami operator, have been developed. These methods
adjust the shape offset by a constant distance, with enough precision.
Nevertheless, these methods fail to conserve sufficient detail because
of the smoothing, a crucial issue which depends on the offset size
\cite{Zhuo2012}. In volumetric approaches, in case of point-based
representations, the offset boundary computation is based on the distance
field and therefore when calculating such offset, the topology of
the model may be different to the original \cite{Chen2011}.

\cite{Gal2009} propose automatic feature detection and shape edition
with feature inter-relationship preservation. They define salient
surface features like ridges and valleys, characerized by their first
and second order curvature derivatives, see \cite{Ohtake2004}, and
angle-based threshold. Likewise, curves have been also classified
as planar or non-planar, approximated by lines, circles, ellipses
and other complex shapes. In such case, the user defines an initial
change over several features which is propagated towards other features,
based on the classified shapes and the inter-relationships between
them. This method works well with objects that have sharp edges, composed
of basic geometric shapes such as lines, circles or ellipses. However,
the method is very limited when models are smooth since it cannot
find the proper features to edit.

Digital sculpting have been traditionally approached either under
a polygonal representation or a voxel grid-based method. Brushes for
inflation operations only depend on the vertex normal \cite{Stanculescu2011}.
In grid-based sculpting, some other operations have allowed to add
or remove voxels since production of polygonal meshes require a processing
of isosurfaces from a volume \cite{Galyean1991}. The drawback comes
from the difficulty of maintaining the surface details during larger
scale deformations.

In the literature, several studies have described the skeleton extraction
systems and different metrics that identify appropriate methods given
an application specific \cite{Attali2007}. One of the best methods
reported in the literature for the extraction of the skeleton is the
Laplacian smoothing method for its advantages of homotopy representation
and hierarchical connections between parts. The Skeleton extraction
methods permits simplify the dimension of the object preserving the
topological structure \cite{Cornea2007}, Au et. al. \cite{Au2008}
present a skeleton extraction method based on iterative smooothing-contraction,
in this method the several constraints are used to waranty that the
process converge to skeleton formed by branchs and joins, the constraints
based on laplacian operator, the low frequencies of the mesh are preserving
with the use of attractor to original mesh, while the iterative smoothin
process remove high frecuencies.

\chapter{Mathematical foundation\label{chap:Mathematical-foundation}}

This chapter studies basic mathematical foundation on differential
geometry to understand the differential operators and the Laplace
beltrami operator.

The differential geometry studies curvatures and geodesics \cite{Hahne2006}.
The differential operators show a deep relationships betwen the geoemetry
(curvatures, geodesics) and topology of the manifold. This differential
operators are very used in applications on computer geometric modelling
over the last years \cite{Rosenberg1997,Alexa2011}.

\section{Manifolds}

A manifold is a topological space $M$ with the following properties:

If $x\in M$, then there is some neighborhood $N\left(x\right)$ and
some integer $n\geq0$ such that $N(x)$ is homeomorphic to $\mathbb{R}^{n}$
\cite{Spivak1-1999}.

This work is related to manifolds that represent a surface in an three-dimensional
Eucliddean Space. This manifolds are homeomorphic to $\mathbb{R}^{2}$.

The manifols are represented by polygonal meshes with points connected
by triangles and quads.

\section{Laplace Operator}

In computer graphics a manifold is often approximated by a discrete
mesh \cite{Ranjan2012}, then is necessary to define a discrete laplacian
operator that act on functions defined on such meshes.

Consider a smooth compact manifold $M$ of dimension $m$ isometrically
embedded in a Euclidean space $\mathbb{R}^{d}$.

Given a twice continuously differentiable function $f\in C^{2}\left(M\right)$,
let $\nabla_{\mbox{M}}f$ denote the gradient vector field of $f$
on $M$.

The Laplace-Beltrami operator $\Delta_{\mbox{M}}$ of $f$ is defined
as the divergence of the gradient; that is \cite{Spivak1-1999},

\noindent \begin{center}
$\frac{\partial^{2}f}{\partial x^{2}}+\frac{\partial^{2}f}{\partial y^{2}}+\frac{\partial^{2}f}{\partial z^{2}}=0$
\par\end{center}

\noindent \begin{center}
$\nabla_{\mbox{M}}^{2}f=\Delta_{\mbox{M}}f=0$
\par\end{center}

\noindent 
\begin{equation}
\Delta_{\mbox{M}}f=div\left(\nabla_{\mbox{M}}f\right)
\end{equation}

\subsection{Discrete Laplace Operator Setting}

Discrete Laplacian operators are linear operators that act on functions
defines on meshes. These functions are specified by their values at
the vertices.

Thus, if a mesh $M$ has $n$ vertices, then functions on $M$ will
be represented by vectors with $n$ components and a mesh Laplacian
will be described by an $n\times n$ matrix \cite{Ranjan2012}.

The Laplacian operator locally takes the difference between the value
of a function at a vertex and a weighted average of its values at
the first-order or one-ring neighbor vertices, then a Laplacian matrix
$L$ has a local form given by

\noindent \begin{center}
$L\left(f\right)_{i}=b_{i}^{-1}\underset{j\in N\left(i\right)}{\sum}w_{ij}\left(f_{i}-f_{j}\right)$
\par\end{center}

Where $w_{ij}$are the weights between the vertex $i$ and the vertex
$j$. $b_{i}^{-1}$ are the factors depending of the boundary region
over vertex $i$. $N\left(i\right)$ are the neighbors that share
a edge with vertex $i$.

\subsection{Gradient of Voronoi Area}

Consider a surface $S$ composed of a set of triangles around vertex
$v_{i}$. Let us define the \textsl{Voronoi Region} of $v_{i}$ as
show in figure \ref{fig:voronoi_region}, The area change produced
by the movement of $v_{i}$ is called the gradient of \textsl{Voronoi
region} \cite{Pinkall1993,Desbrun1999,Meyer2003}.

\noindent 
\begin{align}
\nabla A & =\frac{1}{2}\underset{j}{\sum}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\left(v_{i}-v_{j}\right)\label{eq:eq_gradient_voronoi_area}
\end{align}

\begin{figure}[H]
\includegraphics[width=1\textwidth]{resources/figs/voronoi_region}

\caption{\label{fig:voronoi_region}Area of the Voronoi region around $v_{i}$
in dark blue.$v_{j}$ belong to the first neighborhood around $v_{i}$.
$\alpha_{j}$ and $\beta_{j}$ opposite angles to edge $\protect\overrightarrow{v_{j}-v_{i}}$. }
\end{figure}

If the gradient in equation \ref{eq:eq_gradient_voronoi_area} is
normalized by the total area of the 1-ring neighborhood around $v_{i}$,
the \textsl{discrete mean curvature normal} of a surface $S$ is obtained,
as shown in equation \ref{eq:discrete_mean_curvature_normal}.

\noindent 
\begin{equation}
2\kappa\mathbf{n}=\frac{\nabla A}{A}\label{eq:discrete_mean_curvature_normal}
\end{equation}

\section{Laplace Beltrami Operator}

The \textit{Laplace Beltrami operator} LBO noted as $\Delta$ is used
for measuring the mean curvature normal to the Surface $S$ \cite{Pinkall1993}.

\noindent 
\begin{equation}
\Delta_{\mbox{S}}=2\kappa\mathbf{n}\label{eq:def_LBO}
\end{equation}

\chapter{Proposed Laplacian Operator\label{sec:Proposed-Method}}

This thesis propose an original extension of the Laplace Beltrami
operator for hybrid quad/triangle meshes, mixing arbitrary types of
meshes, exploiting the basic geometrical relationships and ensuring
algorithm convergence.

With the use of the proposed Laplacian Operator this work show succesful
uses in: Smoothing, Enhancing, Smooth Subdivision, Deformation, Sculpting,
and Skeletonization.

\section{Proposed Laplace Beltrami Operator for Hybrid Quad/Triangle Meshes
TQLBO\label{sub:Laplace-Beltrami-operator}}

Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
triangles $T$. The area of $1$-ring neighborhood $A\left(v_{i}\right)$
corresponds to a sum of the areas of the quad faces $A\left(Q_{i}\right)$
and the areas of the triangular faces $\ensuremath{A\left(T_{i}\right)}$
adjacent to vertex $\ensuremath{v_{i}}$.

\noindent \begin{center}
$A\left(v_{i}\right)=A\left(Q_{i}\right)+A\left(T_{i}\right)$ 
\par\end{center}

\begin{figure}[H]
\includegraphics[width=1\columnwidth]{resources/figs/quad_xiong}

\caption{\label{fig:quad_xiong}$t_{j1}^{*}\equiv\vartriangle v_{i}v_{j}v_{j}^{\prime},\, t_{j2}^{*}\equiv\vartriangle v_{i}v_{j}^{\prime}v_{j+1},\, t_{j3}^{*}\equiv\vartriangle v_{i}v_{j}v_{j+1}$
Triangulations of the quad with common vertex $v_{i}$ proposed by
{[}Xiong 2011{]} to define Mean LBO.}
\end{figure}

Applying the mean average area, according to Xiong et. al. \cite{Xiong2011},
from all possible triangulations, as show in figure \ref{fig:quad_xiong},
the area for quads $\ensuremath{A\left(Q_{i}\right)}$ and triangles
$A\left(T_{i}\right)$ is.

\noindent \begin{center}
$A\left(v_{i}\right)=\frac{1}{2^{m}}\overset{m}{\underset{j=1}{\sum}}2^{m-1}A\left(q_{j}\right)+\overset{r}{\underset{k=1}{\sum}}A\left(t_{k}\right)$ 
\par\end{center}

Where $q_{1},q_{2},...,q_{j},...,q_{m}\in Q_{i}$ are quads adjacent
to $v_{i}$, and $t_{1},t_{2},...,t_{k},...,t_{r}\in T_{i}$ are triangles
adjacent to $v_{i}$.

Applying triangulations of the quad with common vertex $v_{i}$ proposed
by \cite{Xiong2011}.

\noindent 
\begin{equation}
A\left(v_{i}\right)=\frac{1}{2}\overset{m}{\underset{j=1}{\sum}}\left[A\left(t_{j1}^{*}\right)+A\left(t_{j2}^{*}\right)+A\left(t_{j3}^{*}\right)\right]+\overset{r}{\underset{k=1}{\sum}}A\left(t_{k}\right)\label{eq:area_1_ring_triangles_quads}
\end{equation}

Applying the gradient operator to (\ref{eq:area_1_ring_triangles_quads}).

\noindent {\small 
\begin{equation}
\nabla A\left(v_{i}\right)=\frac{1}{2}\overset{m}{\underset{j=1}{\sum}}\left[\nabla A\left(t_{j1}^{*}\right)+\nabla A\left(t_{j2}^{*}\right)+\nabla A\left(t_{j3}^{*}\right)\right]+\overset{r}{\underset{k=1}{\sum}}\nabla A\left(t_{k}\right)\label{eq:EqGrad}
\end{equation}
}{\small \par}

According to (\ref{eq:eq_gradient_voronoi_area}), we have.

\noindent \begin{center}
$\nabla A\left(t_{j1}^{*}\right)=\frac{\cot\theta_{j3}\left(v_{j}-v_{i}\right)+\cot\theta_{j2}\left(v_{j}^{\prime}-v_{i}\right)}{2}$ 
\par\end{center}

\noindent \begin{center}
$\nabla A\left(t_{j2}^{*}\right)=\frac{\cot\theta_{j5}\left(v_{j}^{\prime}-v_{i}\right)+\cot\theta_{j4}\left(v_{j+1}-v_{i}\right)}{2}$ 
\par\end{center}

\noindent \begin{center}
$\nabla A\left(t_{j3}^{*}\right)=\frac{\cot\theta_{j6}\left(v_{j}-v_{i}\right)+\cot\theta_{j1}\left(v_{j+1}-v_{i}\right)}{2}$ 
\par\end{center}

\noindent \begin{center}
$\nabla A\left(t_{k}\right)=\frac{\cot\alpha_{k}\left(v_{k}-v_{i}\right)+\cot\beta_{k+1}\left(v_{k+1}-v_{i}\right)}{2}$ 
\par\end{center}

Triangle and quad configurations of the 1-ring neighborhood faces,
adjacent to $v_{i}$, can be simplified to five cases, as shown in
figure \ref{fig:LBO-basic-5-TQ}.

\begin{figure}[H]
\includegraphics[width=1\textwidth]{resources/figs/beltrami}

\caption{\label{fig:LBO-basic-5-TQ}The 5 basic triangle-quad cases with common
vertex $V_{i}$ and the relationship with $V_{j}$ and $V_{j}^{\prime}$.
(a) Two triangles {[}Desbrun 1999{]}. (b) (c) Two quads and one quad
{[}Xiong 2011{]}. (d) (e) Triangles and quads (TQLBO) our contribution.}

\end{figure}

According to equation (\ref{eq:discrete_mean_curvature_normal}),
(\ref{eq:def_LBO}), and five simple cases defined in figure \ref{fig:LBO-basic-5-TQ}
the TQLBO (Triangle-Quad LBO) of $v_{i}$ is.

\noindent 
\begin{equation}
\triangle_{S}\left(v_{i}\right)=2\kappa\mathbf{n}=\frac{\nabla A}{A}=\underset{v_{j}\in N_{1}\left(v_{i}\right)}{\frac{1}{2A}\sum}w_{ij}\left(v_{j}-v_{i}\right)
\end{equation}

\noindent {\small where
\begin{equation}
w_{ij}=\begin{cases}
\left(\cot\alpha_{j}+\cot\beta_{j}\right) & \mbox{case }\mathit{a.}\\
\frac{1}{2}\left(\cot\theta_{\left(j-1\right)1}+\cot\theta_{\left(j-1\right)4}+\cot\theta_{j3}+\cot\theta_{j6}\right) & \mbox{case \ensuremath{\mathit{b}}.}\\
\left(\cot\theta_{j2}+\cot\theta_{j5}\right) & \mbox{case \ensuremath{\mathit{c}}.}\\
\frac{1}{2}\left(\cot\theta_{j3}+\cot\theta_{j6}\right)+\cot\beta_{j} & \mbox{case \ensuremath{\mathit{d}}.}\\
\frac{1}{2}\left(\cot\theta_{\left(j-1\right)1}+\cot\theta_{\left(j-1\right)4}\right)+\cot\alpha_{j} & \mbox{case \ensuremath{\mathit{e}}.}
\end{cases}\label{eq:TQLBO_wij}
\end{equation}
}{\small \par}

We define a Laplacian operator as a matrix equation

\noindent 
\begin{equation}
L\left(i,j\right)=\begin{cases}
-\frac{1}{2A_{i}}w_{ij} & \mbox{if }j\in N\left(v_{i}\right)\\
\frac{1}{2A_{i}}\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij} & \mbox{if }i=j\\
0 & \mbox{otherwise}
\end{cases}\label{eq:TQLBO_Simple_Matrix}
\end{equation}

Where $L$ is a $n\times n$ matrix, $n$ is the number of vertices
of a given mesh $M$, $w_{ij}$ is the TQLBO defined in equation (\ref{eq:TQLBO_wij}),
$N\left(v_{i}\right)$ is the 1-ring neighborhood with shared face
to $v_{i}$, $A_{i}$ is the ring area around $v_{i}$.

Normalized version of the TQLBO as a matrix equation

\noindent 
\begin{equation}
L\left(i,j\right)=\begin{cases}
-\frac{w_{ij}}{\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij}} & \mbox{if }j\in N\left(v_{i}\right)\\
\delta_{ij} & \mbox{otherwise}
\end{cases}\label{eq:TQLBO-Normalized_Matrix}
\end{equation}

Where $\delta_{ij}$ being the Kronecker delta function.

\section{Mesh Smoothing\label{sub:Laplacian-Smooth}}

Computer objects, reconstructed from the real world, are usually noisy.
A common way to attenueate noise in a polygonal mesh is through a
diffusion process \cite{Taubin1995,Desbrun1999}. Laplacian smooth
techniques over a diffusion process allow a proper noise reduction
on the mesh surface with minimal shape changes, while still preserving
a desirable geometry as well as the original shape. The simple idea
is that the vertices are moved in the direction of the Laplacian when
we use the contangent version the vertices are moved in the direction
of the curvature flow. The complexity of Laplacian smoothing can be
linear in time and space with a fast convergence and the diffussion
proccess can attenuate noise with only one iteration due the sparseness
of the laplacian operator.

\noindent 
\begin{equation}
\frac{\partial V}{\partial t}=\lambda L\left(V\right)\label{eq:diffusion_process}
\end{equation}

Where L is the Laplacian matrix defined in equation \ref{eq:TQLBO-Normalized_Matrix}
for meshes with regular sampling, and equation \ref{eq:TQLBO_Simple_Matrix}
for meshes composed by triangles or quads with differents size or
irregular sampling. $\lambda$ is a scalar that control the diffussion
proccess, and smoothing factor.

The equation \ref{eq:diffusion_process} can be linearly approximated
using implicit integration with a Laplacian Operator version of TQLBO,
the use of implicit integration permit the system to be more stability.

\begin{equation}
\left(I-\lambda\partial tL\right)V^{n+1}=V^{n}\label{eq:LaplacianSmoothLinearEquationSystem}
\end{equation}

\section{The Shape Inflation\label{sub:Curvature-Enhancing}}

\begin{figure}[H]
\includegraphics[width=1\textwidth]{resources/figs/teaser_cup}

\caption{\label{fig:Subdivision-Cups} Family of cups generated with our method,
from a coarse model (a), (c): the shape, obtained from the Catmull-Clark
Subdivision (b), (d), is inflated. Soft constraints, over the coarse
model, is drawn in red and blue (c).}
\end{figure}

>>>>

%% LyX 2.1.0 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,letterpaper,english,12pt,english,openany,letterpaper,pagesize]{scrbook}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}
\usepackage{float}
\usepackage{textcomp}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{setspace}
\onehalfspacing

@@

\newcommand{\lyxmathsym}[1]{\ifmmode\begingroup\def\b@ld{bold}
  \text{\ifx\math@version\b@ld\bfseries\fi#1}\endgroup\else#1\fi}

@@

\usepackage{babel}
\begin{document}

\chapter{Mesh Editing with Laplacian Deform\label{sub:Laplacian-Deform}}

This work was accepted and completed for the software Blender \cite{blender}
that is an open source 3D application for modeling, animation, rendering,
compositing, video editing and game creation. In the Google Summer
of Code 2013 program which was administered for Google Inc.

\section{Synopsis}

The mesh editing is generally done with affine transformations, Blender3D
offers some tools to transform the vertices as \textquotedblleft proportional
editing object mode\textquotedblright{} with which the transformation
of some vertices is interpolated to the other vertices connected with
the use of simple distance functions.

This project proposes to implement a method for mesh editing based
on sketching lines defines by user and preserving the geometric details
of the surface.

This method captures the geometric details using a differential coordinates
representations. The differential coordinates captures the local geometric
information (curvature and direction) of the vertex based on its neighbors.
This method allows you to retrieve the best possible original model
after changing the positions of some vertices using the differential
coordinates of the original model.

\section{Benefits to Blender}

This project proposes a new tool for blender user that requires preserve
the geometric details of the surface during a modeling, transformation,
definition of the shape keys of the mesh vertices.

The method will allow novice users to edit any polygon mesh preserving
the surface details.

This method allows the user to define new shape keys in a most fast
and intuitive way.

\section{Deliverables}
\begin{itemize}
\item A new mesh editing tool for Blender. 
\item Some pages of documentation to be included in the manual 
\item A technical document for developers to improve the method in the future. 
\item A tutorial explaining the use of the tool.
\end{itemize}

\section{Project Details}

The project would divide into several parts:
\begin{enumerate}
\item Calculate the differential coordinates. 
\item Store the fixed vertices (Hard constraints). 
\item Store positions of the edited vertices. 
\item Store the more representative vertex for retrieve rotation of every
differential coordinate.
\item Solve the initial solution \textendash{} in least-squares sense. 
\item Rotate the differential coordinates with base on initial solution
and more representative vertex.
\item Reconstruct the surface \textendash{} in least-squares sense. 
\item Generation of the documentation and tutorials.
\end{enumerate}

\section{Project Schedule}
\begin{itemize}
\item 2 Weeks: Calculate the differential coordinates.
\item 2 Weeks: Store the fixed vertexes (Hard constraints).
\item 2 Weeks: Store positions of the edited vertexes.
\item 2 Weeks: Compute initial solution.
\item 2 Weeks: Rotate differential coordinates.
\item 2 Weeks: Reconstruct the surface \textendash{} in least-squares sense. 
\item 1 Weeks: Testing the tool and Define and implement graphical user
integration.
\item 2 Weeks: Generation of the documentation and tutorials.
\end{itemize}

\section{Laplacian Deform}
